Equalizer: A Mature Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
More Collage text
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@12 db7c848b-7755-4df2-b763-8796797afa52

Qt is a popular window system with many application developers. Unfortunately,
it imposes a different threading model for window creation and event handling
then Equalizer. In Equalizer, each GPU rendering thread is independently
responsible for creating its windows, receiving the events and eventually
dispatching them to the application process main thread. This design is
motivated by the natural threading model of X11 and WGL, and allows simple
sequential semantics between OpenGL rendering and event handling. In contrast,
Qt requires all windows and QOpenGLContext to be created from the Qt main
thread. An existing Qt window or context may be moved to a different thread, and
events are signalled from the main thread.

@@

\subsection{Sequel}

@@

@@

\subsection{Swap Synchronization and GPU affinity}

@@

\subsubsection{Tiles and Chunks}

>>>>

Qt is a popular window system with many application developers. Unfortunately,
it imposes a different threading model for window creation and event handling
compared to Equalizer. In Equalizer, each GPU rendering thread is independently
responsible for creating its windows, receiving the events and eventually
dispatching them to the application process main thread. This design is
motivated by the natural threading model of X11 and WGL, and allows simple
sequential semantics between OpenGL rendering and event handling. In contrast,
Qt requires all windows and QOpenGLContext to be created from the Qt main
thread. An existing Qt window or context may be moved to a different thread, and
events are signalled from the main thread.

@@

\subsection{Sequel}\label{sec:sequel}

@@

\subsection{Barriers, Queues and Object Maps}

Collage implements a few generic distributed objects which are used by Equalizer
and applicatons. A barrier is a distributed barrier primitive used for software
swap barriers in Equalizer (\sref{sec:swap}). Its implementation follows a
simple master-slave approach, which has shown to by sufficient for this use
case. Queues are single producer, multiple consumer FIFOs. To hide network
latencies, the consumers use prefetching of queue items into a local queue. They
are used for tile and chunk compounds (\sref{sec:tile}).

The object map facilitates distribution and synchronization of a collection of
distributed objects. Master versions can be registered on a central node, e.g.,
the application node in Equalizer. Consumers, e.g., Equalizer render clients,
can selectively map the objects they are interested in. Committing the object
map will commit all registered objects and sync their new version to the
slaves. Syncing the map on the slaves will synchronize all mapped instances to
the new version recorded in the object map. This effective design allows data
distribution with minimal application logic. It is used by Sequel
(\sref{sec:sequel}) and other Collage applications.

@@

\subsection{Swap Synchronization and GPU affinity}\label{sec:swap}

@@

\subsubsection{Tiles and Chunks}\label{sec:tile}
